\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-27 OaklandSubmission/ld.tex
ld.tex

\divya{Start here...}
\subsubsection*{Circuit semantics} Evaluating a program in the intermediate language produces a
circuit over the secret data to be computed using an \mpc protocol in the distributed setting. With
our circuit semantics, we model the \emph{functional} aspect of a \mpc protocol, parametrized by the sharing functions.

During the circuit evaluation, the wire ranges $r$ are
mapped to (random) strings $b$. The semantics of these strings is
given by pairs of encryption-decryption functions\nc{perhaps call this encode-decode functions since its technically not encryption-decryption? In fact more appropriate might be share-reconstruct, but that would require changing notation so lets not do that.}, written as
$\mathcal{E}_{m}$ and $\mathcal{D}_{m}$ (where $m$ is either
$\mathcal{A}$ or $\mathcal{B}$). More concretely,
$\mathcal{E}_{m}(c)$ returns a pair of two string $b_{1}$ and $b_{2}$
(shares of the two parties), with the property that
$\mathcal{D}_{m}(b_{1}, b_{2}) = c$. We assume that the underlying MPC
protocol instantiates $\mathcal{E}_{m}$ and $\mathcal{D}_{m}$
appropriately.

The circuit semantics is shown in Figure~\ref{fig:cktsem} using the
judgments $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \kappa
\Downarrow b_{1}, b_{2}$, and $\widehat{\rho}_{1}, \widehat{\rho}_{2}
\vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O$,
where $\widehat{\rho}_{1}$ and $\widehat{\rho}_{2}$ are the circuit
environments of the two parties, mapping wire ranges $r$ to strings
$b$. Rule ({\sc{C-Add}}) evinces the pattern for evaluating circuit
gates $\kappa$. To evaluate $\kw{add}\:\kappa_{1}\:\kappa_{2}$, the
rule first evaluates $\kappa_{1}$ to $(b_{11}, b_{21})$ and
$\kappa_{2}$ to $(b_{12}, b_{22})$. Shares $(b_{11}, b_{21})$ are then
combined using $\mathcal{D_{\mathcal{A}}}$ to $n_{1}$, and similarly
$(b_{12}, b_{22})$ are combined to $n_{2}$. The final output of the
\kw{add} gate is then $\mathcal{E}_{\mathcal{A}}(n_{1} + n_{2})$. Note
that this is a functional description of how the \kw{add} gate
evaluates, of course, concretely $n_{1}$ and $n_{2}$ are not observed
by the parties. Rule ({\sc{C-Coerce}}) re-encrypts the shares using the
scheme for $m$. Coming to the evaluation of circuits, the evaluation
of \kw{bind} updates the mapping of $r$ in the input environments, and
the rule ({\sc{C-Out}}) outputs the clear value $c$ to the
observations.

\begin{figure}
  \small
  \fbox{$\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kappa \Downarrow b_{1}, b_{2}$}
  \[
  \\
  \begin{array}{c}
    %% \inferrule*[lab={\footnotesize{C-Wire}}]
    %%            {
    %%              b_{1}, b_{2} = \widehat{\rho_{1}}(r), \widehat{\rho_{2}}(r)
    %%            }
    %%            {
    %%              \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash r \Downarrow b_{1}, b_{2}
    %%            }               
    \inferrule*[lab={\footnotesize{C-In}}]
               {
                 b_{1}, b_{2} = \mathcal{E}_{m}(c)
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{in}^{m}_{j} \Downarrow b_{1}, b_{2}
               }

@@

    \inferrule*[lab={\footnotesize{C-Coerce}}]
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kappa \Downarrow b_{1}, b_{2}\\\\
                 c = \mathcal{D}_{m_{1}}(b_{1}, b_{2})\\\\
                 b'_{1}, b'_{2} = \mathcal{E}_{m}(c)
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kappa \rhd m \Downarrow b'_{1}, b'_{2}
               }
\\\\

    \inferrule*[lab={\footnotesize{C-Add}}]
               {
                 \forall i \in \{1, 2\}.\:\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kappa_{i} \Downarrow b_{1i}, b_{2i}\quad
                 n_{i} = \mathcal{D}_{\mathcal{A}}(b_{1i}, b_{2i})\\\\
                 b_{1}, b_{2} = \mathcal{E}_{\mathcal{A}}(n_{1} + n_{2})
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{add}\:\kappa_{1}\:\kappa_{2} \Downarrow b_{1}, b_{2}
               }

@@

    \inferrule*[lab={\footnotesize{C-Gt}}]
               {
                 \forall i \in \{1, 2\}.\:\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kappa_{i} \Downarrow b_{1i}, b_{2i}\quad
                 n_{i} = \mathcal{D}_{\mathcal{B}}(b_{1i}, b_{2i})\\\\
                 b_{1}, b_{2} = \mathcal{E}_{\mathcal{B}}(n_{1} > n_{2})
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{gt}\:\kappa_{1}\:\kappa_{2} \Downarrow b_{1}, b_{2}
               }

@@

    \inferrule*[lab={\footnotesize{C-Mux}}]
               {
                 \forall i \in \{1, 2, 3\}.\:\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kappa_{i} \Downarrow b_{1i}, b_{2i}\quad
                 c_{i} = \mathcal{D}_{\mathcal{B}}(b_{1i}, b_{2i})\\\\
                 c_{1} = \top \Rightarrow b_{1}, b_{2} = \mathcal{E}_{\mathcal{B}}(c_{2})\quad
                 c_{1} = \bot \Rightarrow b_{1}, b_{2} = \mathcal{E}_{\mathcal{B}}(c_{3})
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{mux}\:\kappa_{1}\:\kappa_{2}\:\kappa_{3} \Downarrow b_{1}, b_{2}
               }

  \end{array}
  \]
  \\\\
    \fbox{$\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \chi \Downarrow \widehat{\rho'_{1}}, \widehat{\rho'_{2}}; O$}
  \[
  \\
  \begin{array}{c}
    \inferrule*[lab={\footnotesize{C-Bind}}]
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kappa \Downarrow b_{1}, b_{2}\\\\
                 \widehat{\rho'_{1}} = \widehat{\rho_{1}}[r \mapsto b_{1}] \quad
                 \widehat{\rho'_{2}} = \widehat{\rho_{2}}[r \mapsto b_{2}]
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{bind}\:\kappa\:r \Downarrow \widehat{\rho'_{1}}, \widehat{\rho'_{2}}; \cdot
               }

@@

    \inferrule*[lab={\footnotesize{C-Out}}]
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kappa \Downarrow b_{1}, b_{2}\\\\
                 c = \mathcal{D}_{m}(b_{1}, b_{2})
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{out}\:\kappa \Downarrow \widehat{\rho_{1}}, \widehat{\rho_{2}}; c
               }
\end{array}
  \]
\caption{Circuit semantics (selected rules)}
\label{fig:cktsem}
\end{figure}

\subsubsection*{Correctness theorem} We first define a judgment for
translation of environments, $\Gamma \vdash \rho \leadsto
\widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$. The
judgment is defined inductively on $\Gamma$, and establishes that
the static environment $\Gamma$ is consistent with the runtime
environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho}_{1}$ and
$\widehat{\rho}_{2}$. As an example, if $x:\kw{uint}^{\mathcal{P}} \in
\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
n$, for some $n$. We elide the judgment, providing the full definition
in the supplementary material.

@@

  \begin{enumerate}
  \item $\Gamma \vdash s \leadsto \widehat{s} \mid \Gamma_{1}$
  \item $\Gamma \vdash \rho \leadsto \widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$
  \end{enumerate}

@@

The theorem states that if a source statement $s$ is well-typed, and
compiles to $\widetilde{s}$, then $s$ terminates in the source
semantics with observations $O_{1}$, $\widetilde{s}$ terminates in the
target semantics with circuit $\chi$, and $\chi$ terminates in the
circuit semantics with observations $O_{2}$, where $O_{1} = O_{2}$
Furthermore, the final environments are also in the compilation
relation.

\nc{Should we point out that the proof of Theorem 1 is provided elsewhere?}
\subsubsection*{Security theorem} The protocols we generate provide
simulation-based security against a semi-honest adversary, in the
framework of ~\cite{gmw,can00,can01}. At a very high level, in this
framework, parties are modeled as non-uniform interactive turing
machines (ITMs), with inputs provided by an environment $\env$. An
adversary $\adv$, selects and ``corrupts'' one of the parties -
however, $\adv$ still follows the protocol specification. $\adv$
interacts with the $\env$, which observes the view of the corrupted
party. At the end of the interaction, $\env$ outputs a single bit. Two
different interactions are defined: the {\em real world} and an {\em
  ideal world}. In the real interaction, the parties run the protocol
$\prot$ in the presence of $\adv$ and $\env$. Let
$\real_{\prot,\adv,\env}$ denote the binary distribution ensemble
describing $\env$'s output in this interaction. In the ideal
interaction, parties send their inputs to an additional entity, a
trusted functionality machine $\F$ that carries the desired
computation truthfully. Let $\simu$ (the simulator) denote the
adversary in this idealized execution, and $\ideal_{\F,\simu,\env}$
the binary distribution ensemble describing $\env$'s output after
interacting with adversary $\simu$ and ideal functionality $\F$. A
protocol $\prot$ is said to {\em securely realize} a functionality
$\F$ if for every adversary $\adv$ in the real interaction, there is
an adversary $\simu$ in the ideal interaction, such that no
environment $\env$, on any input, can tell the real interaction apart
from the ideal interaction, except with negligible probability (in the
security parameter $\secparam$). More precisely, if the two binary
distribution ensembles above are computationally indistinguishable.

We shall assume a cryptographic MPC backend that securely implements any circuit $\chi$ that is output by our compiler. In more detail, this means that for every source program $s$, let $\chi$ be the circuit output by our compiler (as in Theorem \ref{theorem:correctness}). We assume that there exists a two-party secure computation protocol $\prot$ that securely realizes the functionality $\chi$ and we will call the corresponding simulator for the protocol as $\simu_{\tiny{2pc}}$ (that runs on input $\chi$ and the output produced by $\chi$ on the parties inputs). We note that the work of \cite{aby} provides such a protocol $\prot$ and simulator $\simu_{\tiny{2pc}}$ for all circuits $\chi$ output by our compiler. We are now ready to state and prove our security theorem.

\begin{theorem}[Security]\label{theorem:security}
Let $s$ be any functionality or program in our source language with outputs (or observations) $O_1$, that is compiled into a circuit $\chi$ (as defined in Theorem \ref{theorem:correctness}). Let protocol $\prot$ be the two-party secure computation protocol that securely realizes $\chi$ (as defined above). Then, $\prot$ securely realizes $s$.  
\end{theorem}

\noindent {\em Proof.} Our simulator $\simu$ simply runs our compiler on program $s$ to obtain $\chi$ and upon receiving output $O_1$, executes $\simu_{\tiny{2pc}}$ on $\chi$ and $O_1$. Let $O_2$ be the outputs (or observations) of $\chi$. First, from Theorem \ref{theorem:correctness}, we have that the observations in $s$ and $\chi$ are the same (i.e. $O_2 = O_1$). Now, from the security of $\prot$, we have that the simulated view output by $\simu_{\tiny{2pc}}$ (with circuit $\chi$ and output $O_2$) is indistinguishable from the real view of the $\prot$ (when executed on circuit $\chi$ and when the output is $O_2$). Combining these two statements, the proof of the theorem follows. 
\aseem{Can we give a construction of the simulator S in the ideal
  semantics? The simulator S whenever it receives an observable event,
  outputs it to Z, and whenever A receives a string in the real
  semantics, S outputs a random string to Z. Now, with theorem 1,
  observable events are same in the ideal and real semantics, and with
  the security of the crypto backend, the random strings and the
  strings in the protocol are indistinguishable. Is it
  incorrect/naive?

  Also, we should emaphasize here that the ideal semantics is the
  source semantics from Figure x and the real semantics is the circuit
  semantics from Figure y. For the target language semantics, we
  should emphasize that it does not have access to the secrets, so
  there are no observations there.
}

\nc{OK now?}
  %% \\
  %% \[
  %% \begin{array}{rrcl}
  %%   \ftext{Value} & v &::=& c \mid [\overline{c_{i}}]_{n}\\
  %%   \ftext{Observation} & O &::=& \cdot \mid c; O\\
  %% \end{array}
  %% \]

>>>>

\subsubsection*{Circuit semantics} Evaluating a program in the intermediate language produces a
circuit over the secret data to be computed using an \mpc protocol in the distributed setting. With
our circuit semantics, we model the \emph{functional} aspect of a \mpc protocol, parametrized by the sharing functions.

During the circuit evaluation, the wire ranges $r$ are
mapped to (random) strings $b$. The semantics of these strings is
given by pairs of encode-decode algorithms, written as
$\mathcal{E}_{m}$ and $\mathcal{D}_{m}$ (where $m$ is either
$\mathcal{A}$ or $\mathcal{B}$). 
More concretely,
$\mathcal{E}_{m}(c)$ returns a pair of two string $b_{1}$ and $b_{2}$
 with the property that
$\mathcal{D}_{m}(b_{1}, b_{2}) = c$. We assume that the underlying \mpc
protocol instantiates $\mathcal{E}_{m}$ and $\mathcal{D}_{m}$
appropriately. For ABY protocol \cite{aby}, algorithms $(\mathcal{E}_{\mathcal{A}},\mathcal{D}_{\mathcal{A}})$ (resp. $(\mathcal{E}_{\mathcal{B}},\mathcal{D}_{\mathcal{B}})$) correspond to the arithmetic (resp. boolean) sharing and reconstruction algorithms.

\figureref{cktsem} gives the judgements for evaluation of circuit by the two parties using the \mpc protocol. The circuit environment for party $j$ is defined as follows:

\vspace{0.2cm}
$
\small
\begin{array}{rrcl}
    \ftext{Circuit environment} & \widehat\rho_j &::=& \cdot \mid \widehat\rho_j,\wire \mapsto b_j\\
\end{array}
$
\vspace{0.2cm}

\divya{strings $b$ are not formally defined.}

We give the 
judgments $\widehat{\rho}_{1}, \widehat{\rho}_{2} \vdash \gate
\Downarrow b_{1}, b_{2}$, and $\widehat{\rho}_{1}, \widehat{\rho}_{2}
\vdash \chi \Downarrow \widehat{\rho}'_{1}, \widehat{\rho}'_{2}; O$,
where $O$ are the observations (similar to source semantics). 
Rule ({\sc{C-In}}) is used to evaluate the input gate $\kw{in}^{m}_{j}$ that creates the $m$ type shares of the value $c$ input by party $j$.
Rule ({\sc{C-Mult}}) evinces the pattern for evaluating circuit
gates $\gate$. To evaluate $\kw{mult}\:\gate_{1}\:\gate_{2}$, the
rule first evaluates $\gate_{1}$ to $(b_{11}, b_{21})$ and
$\gate_{2}$ to $(b_{12}, b_{22})$. Shares $(b_{11}, b_{21})$ are then
combined using $\mathcal{D_{\mathcal{A}}}$ to $n_{1}$, and similarly
$(b_{12}, b_{22})$ are combined to $n_{2}$. The final output of the
\kw{mult} gate is then $\mathcal{E}_{\mathcal{A}}(n_{1} \mulop n_{2})$. Note
that this is a functional description of how the \kw{mult} gate
evaluates, of course, concretely $n_{1}$ and $n_{2}$ are not observed
by the parties. Rule ({\sc{C-Coerce}}) creates the shares using the
scheme for $m$. Coming to the evaluation of circuits, the evaluation
of \kw{bind} updates the mapping of $\wire$ in the input environments, and
the rule ({\sc{C-Out}}) outputs the clear value $c$ to the
observations.

\begin{figure}
  \small
  \fbox{$\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \gate \Downarrow b_{1}, b_{2}$}
  \[
  \\
  \begin{array}{c}
    %% \inferrule*[lab={\footnotesize{C-Wire}}]
    %%            {
    %%              b_{1}, b_{2} = \widehat{\rho_{1}}(r), \widehat{\rho_{2}}(r)
    %%            }
    %%            {
    %%              \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash r \Downarrow b_{1}, b_{2}
    %%            }               
    \inferrule*[lab={\footnotesize{C-In}}]
               {
                 (b_{1}, b_{2}) = \mathcal{E}_{m}(c)
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{in}^{m}_{j} \Downarrow b_{1}, b_{2}
               }

@@

    \inferrule*[lab={\footnotesize{C-Coerce}}]
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \gate \Downarrow b_{1}, b_{2}\\\\
                 c = \mathcal{D}_{m_{1}}(b_{1}, b_{2})\\\\
                 (b'_{1}, b'_{2}) = \mathcal{E}_{m}(c)
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \gate \rhd m \Downarrow b'_{1}, b'_{2}
               }
\\\\

    \inferrule*[lab={\footnotesize{C-Mult}}]
               {
                 \forall i \in \{1, 2\}.\:\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \gate_{i} \Downarrow b_{1i}, b_{2i}\quad
                 n_{i} = \mathcal{D}_{\mathcal{A}}(b_{1i}, b_{2i})\\\\
                 (b_{1}, b_{2}) = \mathcal{E}_{\mathcal{A}}(n_{1} \mulop n_{2})
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{mult}\:\gate_{1}\:\gate_{2} \Downarrow b_{1}, b_{2}
               }

@@

    \inferrule*[lab={\footnotesize{C-Gt}}]
               {
                 \forall i \in \{1, 2\}.\:\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \gate_{i} \Downarrow b_{1i}, b_{2i}\quad
                 n_{i} = \mathcal{D}_{\mathcal{B}}(b_{1i}, b_{2i})\\\\
                 (b_{1}, b_{2}) = \mathcal{E}_{\mathcal{B}}(n_{1} > n_{2})
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{gt}\:\gate_{1}\:\gate_{2} \Downarrow b_{1}, b_{2}
               }

@@

    \inferrule*[lab={\footnotesize{C-Mux}}]
               {
                 \forall i \in \{1, 2, 3\}.\:\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \gate_{i} \Downarrow b_{1i}, b_{2i}\quad
                 c_{i} = \mathcal{D}_{\mathcal{B}}(b_{1i}, b_{2i})\\\\
                 (c_{1} = \top) \Rightarrow \left((b_{1}, b_{2}) = \mathcal{E}_{\mathcal{B}}(c_{2})\right)\hspace{0.1cm}
                 (c_{1} = \bot) \Rightarrow \left((b_{1}, b_{2}) = \mathcal{E}_{\mathcal{B}}(c_{3})\right)
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{mux}\:\gate_{1}\:\gate_{2}\:\gate_{3} \Downarrow b_{1}, b_{2}
               }

  \end{array}
  \]
  \\\\
    \fbox{$\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \crct \Downarrow \widehat{\rho'_{1}}, \widehat{\rho'_{2}}; O$}
  \[
  \\
  \begin{array}{c}
    \inferrule*[lab={\footnotesize{C-Bind}}]
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \gate \Downarrow b_{1}, b_{2}\\\\
                 \widehat{\rho'_{1}} = \widehat{\rho_{1}}[\wire \mapsto b_{1}] \quad
                 \widehat{\rho'_{2}} = \widehat{\rho_{2}}[\wire \mapsto b_{2}]
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{bind}\:\gate\:\wire \Downarrow \widehat{\rho'_{1}}, \widehat{\rho'_{2}}; \cdot
               }

@@

    \inferrule*[lab={\footnotesize{C-Out}}]
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \gate \Downarrow b_{1}, b_{2}\\\\
                 c = \mathcal{D}_{m}(b_{1}, b_{2})
               }
               {
                 \widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \kw{out}\:\gate \Downarrow \widehat{\rho_{1}}, \widehat{\rho_{2}}; c
               }
\end{array}
  \]
\caption{Circuit semantics (selected rules)}
\label{fig:cktsem}
\end{figure}

\subsubsection*{Correctness theorem} We first define a judgment for
translation of environments, $\Gamma \vdash \rho \leadsto
\widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$. The
judgment is defined inductively on $\Gamma$, and establishes that
the static environment $\Gamma$ is consistent with the runtime
environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho}_{1}$ and
$\widehat{\rho}_{2}$. As an example, if $x:\kw{uint}^{\mathcal{P}} \in
\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
n$, for some $n$. \divya{This judgement is not clear. If I am correct, it says that for public values $\rho$ and $\widetilde{\rho}$ are consistent and for secret values $\rho$ has values and $\widehat{rho}_j$ contain shares.} We elide the judgment, providing the full definition
in the supplementary material.

@@

  \begin{enumerate}
  \item $\Gamma \vdash s \leadsto \widetilde{s} \mid \Gamma_{1}$
  \item $\Gamma \vdash \rho \leadsto \widetilde{\rho}; \widehat{\rho}_{1}, \widehat{\rho}_{2}$
  \end{enumerate}

@@

The theorem states that if a source statement $s$ is well-typed, and
compiles to $\widetilde{s}$ in intermediate language, then $s$ terminates in the source
semantics with observations $O_{1}$, $\widetilde{s}$ evaluates to circuit $\crct$, and $\crct$ terminates in the
circuit semantics with observations $O_{2}$, where $O_{1} = O_{2}$
Furthermore, the final environments are also in the compilation
relation. \divya{Should we call the judgement between environs as compilation relation?}
Due to space reasons, we provide the proof in \cite{anonymized}.
